### 2020-02-12 msr.tex
msr features section edit

As mentioned in the introduction section, the most significant difference
between \glspl{MSR} and other reactor concepts is the liquid fuel in
\glspl{MSR}; fissile and/or fertile material is dissolved in high temperature,
commonly eutectic mixtures of molten salts. Most \gls{MSR} designs are
circulating-fuel reactors. The primary coolant loop containing the fuel salt
transfers heat through a heat exchanger to the clean, secondary/intermediate
loop.

The flexibility of \glspl{MSR} is best illustrated by the various designs
under development today. Graphite-moderated thermal-spectrum \glspl{MSR} are
typically straight-forward \gls{LEU} burners, or $^{232}$Th/$^{233}$U
breeders, while epithermal- and fast-spectrum \glspl{MSR} have the additional
options of operating as \gls{TRU} fuel burners or $^{238}$U/$^{239}$Pu
breeders. Breeder designs can be further categorized into one- or two-fluid
designs; two-fluid designs feature blanket molten salt mixtures that contain
higher proportions of fertile material than the fuel salt mixture.

>>>>

As mentioned in the introduction section, the most significant difference
between \glspl{MSR} and other reactor concepts is the liquid fuel in
\glspl{MSR}; fissile and/or fertile material is dissolved in high temperature,
commonly eutectic mixtures of molten salts. Most \gls{MSR} designs are
circulating-fuel reactors. The primary coolant loop containing the fuel salt
transfers heat through a heat exchanger to the clean, secondary/intermediate
loop. The liquid fuel form allows for continuous online fuel reprocessing,
and the removal of gaseous \glspl{FP} via a gas sparging system.

The flexibility of \glspl{MSR} is best illustrated by the various designs
under development today. Graphite-moderated thermal-spectrum \glspl{MSR} are
typically straight-forward \gls{LEU} burners, or $^{232}$Th/$^{233}$U
iso-breeders/breeders, while epithermal- and fast-spectrum \glspl{MSR} have
the additional options of operating as \gls{TRU} fuel burners or
$^{238}$U/$^{239}$Pu breeders. Breeder designs can be further categorized into
one- or two-fluid designs; two-fluid designs feature separate blanket molten
salt mixtures that contain higher proportions of fertile material than the
fuel salt mixture.

\subsection{Safety}

\glspl{MSR} hold a number of safety advantages over current \glspl{LWR}. The
most immediate and significant advantage is the strong negative temperature
reactivity feedback of the fuel salt. This is due to greater
temperature-induced density changes in liquid fuel than solid fuel. Combined
with the Doppler broadening of resonance capture cross sections present in
both fuel forms, we expect to observe a smaller temperature increase following
an unprotected reactivity insertion. The overall temperature reactivity
coefficient varies widely between different \gls{MSR} designs due to other
structures, such as moderators and reflectors, present in the core. In
particular, graphite moderators tend to have slightly positive temperature
reactivity coefficients. This was notably observed in the \gls{MSBR} concept,
but the total temperature reactivity coefficient was still relatively large
and negative.

Continuous online fuel reprocessing allows operators to maintain low excess
reactivity inventories in the core as additional fuel can be added on an ad
hoc basis. This factor, in addition to the strong negative temperature
reactivity coefficient, diminishes the likelihood and severity of unprotected
criticality accidents in \glspl{MSR}.
